Hou10ni Profiling with TAU

### 2017-06-19 hou10ni/Tutorial/hou10ni_profile.tex
Hou10ni's kernel : Clean

class Experiment

 def self.run()
  k_ref_params = {:kernel => :ref, :preprocessor => false, :LDFLAGS => "-lgfortran", :FCFLAGS => "-fbounds-check"}

  set_lang(FORTRAN)
  kernels={}

  # Creating ref kernel
  kernels[k_ref_params] = KRef::new(k_ref_params)
  kernels[k_ref_params].generate
 # Building ref kernel
  puts kernels[k_ref_params].kernel
  kernels[k_ref_params].kernel.build(:LDFLAGS => k_ref_params[:LDFLAGS], :FCFLAGS => k_ref_params[:FCFLAGS] )

  # Parameters for loop iteration 1 and MPI Process 0 (in the directory fluid_inner_elt_ref/sub_time_loop_1/)
  inputs = kernels[k_ref_params].kernel.load_ref_inputs()
  puts "** inputs =", inputs

  inputs.each_key { |key|
    puts key
    puts kernels[k_ref_params].kernel.run(*(inputs[key])).inspect
    puts kernels[k_ref_params].kernel.compare_ref(outputs[key], inputs[key]).inspect
  }

  return kernels
 end
end

Experiment.run
\end{lstlisting}

@@

  @opts = {:preprocessor => false, :unroll => false, :inline => :included}
  @opts.update(options)

  # Parameters 
  @Nflu_inner         = Int("Nflu_inner", :dir => :in )
  @Nflusol_inner      = Int("Nflusol_inner", :dir => :in )
  @nb_rhs             = Int("nb_rhs", :dir => :in )
  @afluSize           = Int("afluSize", :dir => :in )
  @pSize              = Int("pSize", :dir => :in )
  @vecSize_1          = Int("vecSize_1", :dir => :in )
  @vecSize_2          = Int("vecSize_2", :dir => :in )
  @matSize            = Int("matSize", :dir => :in )

  @idx_vec_flu        = Int("idx_vec_flu", :dir => :in, :dim => [Dim(@vecSize_1),Dim(@vecSize_2)] )
  @idx_mat_flu        = Int("idx_mat_flu", :dir => :in, :dim => [Dim(@matSize)] )
  @P_new              = Real("P_new",:dir => :inout, :dim => [Dim(@pSize),Dim(@nb_rhs)])
  @P_inter            = Real("P_inter",:dir => :in, :dim => [Dim(@pSize),Dim(@nb_rhs)])
  @P_old              = Real("P_old",:dir => :in, :dim => [Dim(@pSize),Dim(@nb_rhs)])
  @A_flu              = Real("A_flu",:dir => :in, :dim => [Dim(@afluSize)])

@@

    #..  FUNCTIONS ..#
    register_funccall("matmul") if get_lang == FORTRAN
    call_matmul = lambda{|x,y|
      if get_lang == FORTRAN
        return matmul(x,y)
      end
    }

@@

class Experiment

 def self.run()

 # set_default_int_size(8)
  set_default_real_size(4)
  k_boast_params = {:kernel => :boast, :preprocessor => false, :LDFLAGS => "-lgfortran", :FCFLAGS => "-fbounds-check -fimplicit-none"}

  set_lang(FORTRAN)
  kernels = {}
  stats_svg = {}
  stats = []
  repeat = 3

  # Creating ref kernel
  kernels[k_boast_params] = KBoast::new(k_boast_params)
  kernels[k_boast_params].generate
  puts "*********** Building kernel ***********\n"
  puts kernels[k_boast_params].kernel
  kernels[k_boast_params].kernel.build(:LDFLAGS => k_boast_params[:LDFLAGS], :FCFLAGS => k_boast_params[:FCFLAGS] )

  puts "\n*********** Testing boast kernel with inputs parameters ***********\n"
  inputs = kernels[k_boast_params].kernel.load_ref_inputs()
  outputs = kernels[k_boast_params].kernel.load_ref_outputs()

  repeat.times {
    inputs.each_key { |key|
      puts key
      stats.push kernels[k_boast_params].kernel.run(*(inputs[key]))
      puts kernels[k_boast_params].kernel.run(*(inputs[key])).inspect
      puts kernels[k_boast_params].kernel.compare_ref(outputs[key], inputs[key]).inspect
    }
  }
  stats.sort_by! { |a| a[:duration] }
  stats = stats.first

  puts "#{kernels[k_boast_params].kernel.procedure.name}: #{stats[:duration]} s ->  #{stats[:duration]*1.0e3} ms"
  return kernels
 end
end

Experiment.run
\end{lstlisting}

@@

*********** Testing boast kernel with inputs parameters ***********
./fluid_inner_elt_boast/sub_time_loop_1
{:duration=>0.13263683, :start=>-4004705691753970176, :end=>-3872068861753970176}
{"P_new"=>0.0}
./fluid_inner_elt_boast/sub_time_loop_1
{:duration=>0.140625219, :start=>-3642235174753970176, :end=>-3501609955753970176}
{"P_new"=>0.0}
./fluid_inner_elt_boast/sub_time_loop_1
{:duration=>0.147113606, :start=>-3274643277753970176, :end=>-3127529671753970176}
{"P_new"=>0.0}
fluid_inner_elt_boast: 0.15179012 s ->  151.79012 ms  
\end{lstlisting}

\subsubsection*{Optimisations}

>>>>

 set_lang(FORTRAN)

# Creating ref kernel
k_ref_params = {:kernel => :ref, :LDFLAGS => "-lgfortran", :FCFLAGS => "-fbounds-check -O2"}
k = KRef::new(k_ref_params)
k.generate
puts k.kernel
k.kernel.build(:LDFLAGS => k_ref_params[:LDFLAGS], :FCFLAGS => k_ref_params[:FCFLAGS] )

# Parameters for loop iteration 1 and MPI Process 0 
# in the directory fluid_inner_elt_ref/sub_time_loop_1/
inputs = k.kernel.load_ref_inputs()
puts "** inputs =", inputs

inputs.each_key { |key|
  puts k.kernel.run(*(inputs[key]))
  puts k.kernel.compare_ref(outputs[key], inputs[key]).inspect
}

puts "Testing done\n"
\end{lstlisting}

@@

  # Parameters 
  @Nflu_inner         = Int("Nflu_inner", :dir => :in )
  @Nflusol_inner      = Int("Nflusol_inner", :dir => :in )
  @nb_rhs             = Int("nb_rhs", :dir => :in )
  @afluSize           = Int("afluSize", :dir => :in )
  @pSize              = Int("pSize", :dir => :in )
  @vecSize_1          = Int("vecSize_1", :dir => :in )
  @vecSize_2          = Int("vecSize_2", :dir => :in )
  @matSize            = Int("matSize", :dir => :in )
  @idx_vec_flu        = Int("idx_vec_flu", :dir => :in, :dim => [Dim(@vecSize_1),Dim(@vecSize_2)] )
  @idx_mat_flu        = Int("idx_mat_flu", :dir => :in, :dim => [Dim(@matSize)] )
  @P_new              = Real("P_new",:dir => :inout, :dim => [Dim(@pSize),Dim(@nb_rhs)])
  @P_inter            = Real("P_inter",:dir => :in, :dim => [Dim(@pSize),Dim(@nb_rhs)])
  @P_old              = Real("P_old",:dir => :in, :dim => [Dim(@pSize),Dim(@nb_rhs)])
  @A_flu              = Real("A_flu",:dir => :in, :dim => [Dim(@afluSize)])

@@

    #..  FUNCTIONS ..#
    register_funccall("matmul") if get_lang == FORTRAN
    call_matmul = lambda{|x,y|
        return matmul(x,y)
    }

@@

set_default_real_size(4)

k_boast_params = {:kernel => :boast, :LDFLAGS => "-lgfortran", :FCFLAGS => "-fbounds-check -fimplicit-none -O2"}

set_lang(FORTRAN)
stats = []
repeat = 5

# Creating boast kernel
k = KBoast::new(k_boast_params)
k.generate
puts k.kernel
k.kernel.build(:LDFLAGS => k_boast_params[:LDFLAGS], :FCFLAGS => k_boast_params[:FCFLAGS] )

inputs = k.kernel.load_ref_inputs()
outputs = k.kernel.load_ref_outputs()

inputs.each_key { |key|
  repeat.times {
    stats.push k.kernel.run(*(inputs[key]))
  }
  puts k.kernel.compare_ref(outputs[key], inputs[key]).inspect
}

stats.sort_by! { |a| a[:duration] }
p stats
stats = stats.first

puts "#{k.kernel.procedure.name}: optim_nested = #{k_boast_params[:optim_nested]}  #{stats[:duration]} s ->  #{stats[:duration]*1.0e3} ms"
\end{lstlisting}

@@

{"P_new"=>0.0}
[{:duration=>0.011553553000000001, :start=>-8096482666880853504, :end=>-8084929113880853504}, {:duration=>0.011923121, :start=>-8122491033880853504, :end=>-8110567912880853504}, {:duration=>0.013262399000000001, :start=>-8135791916880853504, :end=>-8122529517880853504}, {:duration=>0.013991319, :start=>-8110525936880853504, :end=>-8096534617880853504}, {:duration=>0.014984313, :start=>-8150824959880853504, :end=>-8135840646880853504}]
fluid_inner_elt_boast: optim_nested = 3  0.011553553000000001 s ->  11.553553 ms
\end{lstlisting}

\subsection{Optimisations}

Unroll both loops.

  @opts = {:optim_nested => 1, :optim_main => 1}
  @opts.update(options)

  # Parameters 
  @Nflu_inner         = Int("Nflu_inner", :dir => :in )
  @Nflusol_inner      = Int("Nflusol_inner", :dir => :in )
  @nb_rhs             = Int("nb_rhs", :dir => :in )
  @afluSize           = Int("afluSize", :dir => :in )
  @pSize              = Int("pSize", :dir => :in )
  @vecSize_1          = Int("vecSize_1", :dir => :in )
  @vecSize_2          = Int("vecSize_2", :dir => :in )
  @matSize            = Int("matSize", :dir => :in )
  @idx_vec_flu        = Int("idx_vec_flu", :dir => :in, :dim => [Dim(@vecSize_1),Dim(@vecSize_2)] )
  @idx_mat_flu        = Int("idx_mat_flu", :dir => :in, :dim => [Dim(@matSize)] )
  @P_new              = Real("P_new",:dir => :inout, :dim => [Dim(@pSize),Dim(@nb_rhs)])
  @P_inter            = Real("P_inter",:dir => :in, :dim => [Dim(@pSize),Dim(@nb_rhs)])
  @P_old              = Real("P_old",:dir => :in, :dim => [Dim(@pSize),Dim(@nb_rhs)])
  @A_flu              = Real("A_flu",:dir => :in, :dim => [Dim(@afluSize)])

    #..  FUNCTIONS ..#

    register_funccall("matmul") if get_lang == FORTRAN
    call_matmul = lambda{|x,y|
        return matmul(x,y)
    }

    register_funccall(:modulo) if get_lang == FORTRAN

    jmax = Variable::new('jmax', Int)
    imax = Variable::new('imax', Int)

    decl i,j,i_tmp1,i_tmp2, i1,i2,i3,i4,p_aux
    decl jmax,imax

    ##.. Nested loop optimization
    optim_1 = lambda { |unroll,i|
      loop_1 = lambda { |indice|
        pr i1 === @idx_vec_flu[2*indice,i]
        pr i2 === @idx_vec_flu[2*indice+1,i]
        pr i_tmp2 === i_tmp1 + i2 - i1
        pr p_aux.slice(i_tmp1..i_tmp2,1..@nb_rhs) === @P_inter.slice(i1..i2,1..@nb_rhs)
        pr i_tmp1 === i_tmp2 + 1.to_var
      }

      pr jmax === @idx_vec_flu[1,i]-(unroll-1)
      f_nested = For(j,1,jmax, step: unroll){
        unroll.times { |k|
          loop_1[j+k]
        }
      }
      f_arr_nested = [f_nested]
      if unroll > 1 then
          f2_nested = For(j,(@idx_vec_flu[1,i]-modulo(@idx_vec_flu[1,i],unroll))+1, @idx_vec_flu[1,i]){
            loop_1[j]
          }
          f_arr_nested.push f2_nested
      end
      f_arr_nested
   }

    ##.. Main loop optimization
    optim_2 = lambda { |unroll|
      loop_2 = lambda { |indice|
        pr i_tmp1 === 1
        # Nested loop optimized - No optimization -> = optim_1[1,indice].each{ |f|  pr f }
        optim_1[@opts[:optim_nested],indice].each { |f_nested|
          pr f_nested
        }
        pr i1 === @idx_vec_flu[2,indice]
        pr i2 === @idx_vec_flu[3,indice]
        pr i3 === @idx_mat_flu[indice]
        pr i4 === @idx_mat_flu[indice+1] - 1
        reshape_code ="RESHAPE(#{@A_flu.slice(i3..i4)}, (/#{i2}-#{i1}+1, #{i_tmp2}/))"
        pr @P_new.slice(i1..i2,1..@nb_rhs) === call_matmul.call(reshape_code , p_aux.slice(1..i_tmp2,1..@nb_rhs) ) - @P_old.slice(i1..i2,1..@nb_rhs)
      }

      pr imax === @Nflu_inner+@Nflusol_inner-(unroll-1)
      f_main = For(i,1,imax, step: unroll){
        unroll.times { |k|
          loop_2[i+k]
        }
      }
      f_arr_main = [f_main]
      if unroll > 1 then
        f2_main = For(i,(@Nflu_inner+@Nflusol_inner-modulo(@Nflu_inner+@Nflusol_inner,unroll))+1, @Nflu_inner+@Nflusol_inner){
          loop_2[i]
        }
        f_arr_main.push f2_main
      end
      f_arr_main
    }

    ## Procedure
    optim_2[@opts[:optim_main]].each { |f_main|
        pr f_main
    }

    close @kernel.procedure
   }
